---
title: "lab_report_knapsack"
author: "Sarah Alsaadi and Nastaran Meftahi"
date: "11/22/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{API-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab Report Knapsack

This vignette contains the lab report.

## Brute force

Question: How much time does it take to run the algorithm for n = 16 objects?

Answer: bruteforce: 0.308 sec elapsed

```{r eval=FALSE}
library("tictoc")
tic("bruteforce")
bfk <- brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
toc()
```

## Dynamic programming

Question: How much time does it take to run the algorithm for n = 500 objects? 

Answer: dynamicprogramming: 0.75 sec elapsed

```{r eval=FALSE}
tic("dynamicprogramming")
bfk <- dynamic_knapsack(x = knapsack_objects[1:500,], W = 3500)
toc()
```

## Greedy heuristic

Question: How much time does it take to run the algorithm for n = 1.000.000 objects?

Answer: greedyheuristic: 0.177 sec elapsed

```{r eval=FALSE}
tic("greedyheuristic")
bfk <- greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500)
toc()
```

## Code profiling and optimization

Question: What performance gain could you get by trying to improve your code?

Answer: We have used the profvis package to profile our code for all 3 approaches (see R/profiling/profvis.R). Since the code was fairly simple/straight forward, we didn't manage to optimize it any further. However, the profiling tool showed us where most of the time is spent.

### Brute force

In the brute force approach, the most time consuming is the line 
```{r eval=FALSE} elements<-as.integer(intToBits(i))[1:n]```. We tried to find a better way to do this, but we were unsuccessful.

### Dynamic programming

In the dynaminc programming approach, most of the time is spent on lines 28 and 35 (see the dynamicprogramming-profile.Rprofvis in the vignettes folder). However, we didn't manage to write faster code in this case either.

### Greedy approach

The greedy approach is generally very fast. No improvements were found.

## Parallelize brute force

Question: What performance gain could you get by parallelizing the brute force search?

Answer: bruteforce: 1.905 sec elapsed

```{r eval=FALSE}
tic("bruteforce")
bfk <- brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel = TRUE)
toc()
```

As seen above, the time for the parallel implementation is higher than before. We don't know if this might have to do with the overhead introduced by the calls to the parallel package or something in our particular implementation.