---
title: "lab_report_knapsack"
author: "Sarah Alsaadi and Nastaran Meftahi"
date: "11/22/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{API-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Lab Report Knapsack

This vignette contains the lab report.

## Brute force

Question: How much time does it take to run the algorithm for n = 16 objects?

Answer: bruteforce: 0.308 sec elapsed

```{r eval=FALSE}
library("tictoc")
tic("bruteforce")
bfk <- brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
toc()
```

## Dynamic programming

Question: How much time does it take to run the algorithm for n = 500 objects? 

Answer: dynamicprogramming: 0.75 sec elapsed

```{r eval=FALSE}
tic("dynamicprogramming")
bfk <- dynamic_knapsack(x = knapsack_objects[1:500,], W = 3500)
toc()
```

## Greedy heuristic

Question: How much time does it take to run the algorithm for n = 1.000.000 objects?

Answer: greedyheuristic: 0.177 sec elapsed

```{r eval=FALSE}
tic("greedyheuristic")
bfk <- greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500)
toc()
```

## Code profiling and optimization

Question: What performance gain could you get by trying to improve your code?

Answer: 

## Parallelize brute force

Question: What performance gain could you get by parallelizing the brute force search?

Answer: bruteforce: 1.905 sec elapsed

```{r eval=FALSE}
tic("bruteforce")
bfk <- brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel = TRUE)
toc()
```

As seen above, the time for the parallel implementation is higher than before. We don't know if this might have to do with the overhead introduced by the calls to the parallel package or something in our particular implementation.